Delta Factor - A New Authorization Factor

### 2022-08-07 paper1.tex
More FINAL paper updates

\section{Abstract}
TBA (As per professor) %This is modus operandi bc as the paper evolves, the abstract changes invariably
\section{Introduction}
\setlength{\baselineskip}{1.5\baselineskip}
\indent

@@

\section{Related Work}
Catching Transparent Phish: Analyzing and Detecting MITM Phishing Toolkits (2021, ACM Conference on Computer and Communications Security)
Brian Kondracki, Babak Amin Azad, Oleksii Starov, Nick Nikiforakis.\\

@@

%---------------------------------------

\section{Design Principles}
MITM Phishing TOOLkitS:\\
PHOCA - by our SUNY - Stonybrook research group\\
Evilginx, Muraena, and Modlishka \\

@@

% Paragraph 2: introduction of DT techniques ...

% Paragraph 6: introduction of RF techniques

>>>>

%---------------------------------------------------------------------------------------------------------------------
\section{Abstract}
TBA (As per professor) %This is modus operandi bc as the paper evolves, the abstract changes invariably
\section{Introduction}
\setlength{\baselineskip}{1.5\baselineskip}
\indent

@@

%---------------------------------------------------------------------------------------------------------------------
\section{Related Work}
Catching Transparent Phish: Analyzing and Detecting MITM Phishing Toolkits (2021, ACM Conference on Computer and Communications Security)
Brian Kondracki, Babak Amin Azad, Oleksii Starov, Nick Nikiforakis.\\

@@

%---------------------------------------------------------------------------------------------------------------------
\section{Design Principles}
MITM Phishing TOOLkitS:\\
PHOCA - by our SUNY - Stonybrook research group\\
Evilginx, Muraena, and Modlishka \\

@@

% Paragraph 2,3,...: introduction of DT techniques ... [Actually - Inspiration]
\noindent Inspired by an existing movement, a growing trend towards multi factor authentication
identified that most methods still only do knowledge-based or device-based validation.
This is by incorporating existing and standardized One-Time Passcode technology, with connection-oriented details (ie., COTP)
to produce a method to offer an authentication stronger than knowledge-based alone. This empowers users to detect the most advanced MITMs today.\\

\noindent
How the Delta factor works:\\
Since most authentication methods can be mitigated by applying modern phishing toolkits,
they can be detected through \textit{network traffic}.
There are numerous methods to validate the user through various methods, but \textit{few \textbf{server} authentication methods}.
We propose reverse 2FA authentication method to \textbf{validate the server from the client perspective}.
We to want validate the link between the server plus client, by fingerprinting common \textbf{connection} details and independently verifying shared secrets.\\

% Paragraph 6: introduction of RF techniques 		[Actually Delta factor/COTP]
\noindent
A synopsis on \textbf{COTP} is created by:\\
\noindent
A high e, (entropy) shared secret,\\
extraction of shared low level network features,\\
creating a shared time frame,\\ 
creating a composite secret from from the features and high-e secret,\\
generating a hash from the composite secret,\\
% Compress/Truncate hash, Yielding a Connection_based OTP
having the \textit{server} send the generated COTP, and\\
comparing the client and server COTPs. At this point, the connection is accepted or declined.\\

\noindent
The Implementation Details are design goals, high-level limitations, implementation details on the server side as well as the client side, and system integration\\

% frame 16 - Interesting Implementation Limitations

%--------------------------------------------------------------------------------------------------------------------
\section{Measurements}
% TBA
TBA\\
TBA\\
